### 2024-10-10 Article/main.tex
minori

\begin{prop}\label{prop:ext_left_to_funct}
    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
\end{prop}

\begin{proof}
    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}. It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$ such that: $R(L(f)) \circ \eta_X = \eta_Y \circ f$.
\end{proof}

@@

\begin{proof}

@@

\section{Universal Constructions}\label{sect:univ_constr}

% What we are interested in are the "best" construction having a certain property, and we exprtess this fact via requiring unique factorization when another construction does

>>>>

\begin{prop}\label{prop:ext_left_to_funct}
    In \Cref{def:right_adjoint}, the map that takes an object $A$ to an object $L(A)$ can be extended to a functor $L: \cat{D \rightarrow C}$.
\end{prop}
\todo{Devi mostrare che eta risulta naturale (viene in automatico ma conviene scriverlo per la dimostrazione successiva).}
\begin{proof}
    Let $R$ be the right adjoint as in ~\Cref{def:right_adjoint}. It is possible to define, for $f: X \rightarrow Y$, $L(f) : L(X) \rightarrow L(Y)$  such that: \[R(L(f)) \circ \eta_X = \eta_Y \circ f\] \todo{finire}
\end{proof}

@@

\begin{proof}
	Given an object $B$ in $\cat{C}$, we can consider the solid part of the diagram below. 
	Since $R$ is a right adjoint, we get a unique arrow whose image through $R$ make the triangle commutative.
	    \[
	\begin{tikzcd}
		R(B)\arrow[r, "{\eta_{R(B)}}"] \arrow[dr, "id_{R(B)}" swap] & R(L(R(B))) \arrow[d, dashed, "R(\epsilon_B)"] \\
		& R(B)
	\end{tikzcd}
	\]

	Let now $A$ be an object of $\cat{D}$ and $g\colon L(A)\to B$ an arrow in $\cat{C}$. We can consider the composite $R(g)\circ \eta_A\colon A\to R(B)$. Then we have
	\begin{align*}
		R(\epsilon_B)\circ R(L(R(g)))\circ R(L(\eta_A))\circ \eta_A&=R(\epsilon_B)\circ R(RL(R(g)))\circ \eta_{R(L(A))}\circ \eta_A\\&=R(\epsilon_B)\circ \eta_{R(B)}\circ R(g)\circ \eta_A\\&=R(g)\circ \eta_A
	\end{align*}
	Since $R$ is a right adjoint and $\eta$ its unit, it follows that $\epsilon_B\circ L(R(g)\circ \eta_A)$ coincides with $g$ as wanted.
 \end{proof}

@@

\section{Universal Constructions}\label{sect:univ_constr}
\todo{Questa è da riscriviere e ridurre}
% What we are interested in are the "best" construction having a certain property, and we exprtess this fact via requiring unique factorization when another construction does
